### 2025-04-15 project2/nnMetamodels.tex
Update nnMetamodels.tex

\gls{dnn} have attracted attentions of researchers and practitioners due to their success~\citep{hastie2009elements,lecun2015deep} in solving real-world machine learning tasks such as AlphaGo~\citep{silver2016mastering} and ChatGPT~\citep{chatgpt}.
Since the first artificial neural network model~\citep{mcculloch1943logical} and the first algorithm for training a perceptron~\citep{rosenblatt1958perceptron}, especially after the introduction of backpropagation~\citep{rumelhart1985learning} and the growth of high-performance computing, the field of artificial neural network and deep learning in general has been growing rapidly.
Two specialized neural network architectures that are relevant to our study are \gls{rnn}~\citep{williams1989learning,sutskever2014sequence} and \gls{lstm}~\citep{hochreiter1997long,chung2014empirical}.
In the field of actuarial science, a metamodel is commonly referred to as a proxy model.
Despite their success, \gls{dnn} models are often criticized for their lack of transparency and interpretability, which hinders their adoption in financial and actuarial applications.
Enormous research efforts have been spent to test and improve the robustness of \gls{dnn} models with carefully designed noise injection methods.
~\cite{poole2014analyzing} show that injecting synthetic noise before and after hidden unit activations during training improves the performance of autoencoders.
~\cite{neelakantan2015adding} improve learning for \gls{dnn}s by injecting synthetic noise to the gradients during backpropagations.
A branch of research has been devoted to understanding the resilience of neural network models to noise in training labels.
For example,~\cite{luo2016understanding} show that adding synthetic label noise to the convolutional neural network (\gls{cnn}) can improve its ability to capture global features. 
~\cite{srivastava2014dropout} quantify the error tolerance by injecting synthetic label noise with a custom Boltzmann machine hardware.
~\cite{szegedy2013intriguing} find that neural networks are vulnerable to adversarial examples, and~\cite{goodfellow2014explaining} design an efficient method to generate such noisy examples to exploit the vulnerability to adversarial perturbations.
~\cite{carlini2017towards} design targeted attacks to training labels to test the robustness of neural networks. 
Instead of using synthetic noise, ~\cite{jiang2020beyond} inject real-world label noise and examine noise tolerance of neural networks with controlled noise levels.
The aforementioned studies use real-world data, as is typically the case for many neural network studies, where noise is already present in the training labels before any noise injection.
Users of real-world data have little control over the noise level of the original training labels and usually examine the effect of noisy data by injecting noise, but it is unclear whether a neural network model trained on noisy data actually learns the real, i.e., noiseless, feature-label relationship.
Due to their lack of transparency and interpretability, the adoption of \gls{dnn}s in financial and actuarial applications has been received by regulators with some skepticism.

@@

In a nested simulation, a simulation model is used to generate a large number of outer scenarios, and each scenario is then used as an input to another simulation model, referred to as an inner simulation model.
Borrowing terminologies from the machine learning community, we can view a set of simulated outer scenarios and estimated hedging errors for those scenarios as \textit{features} and noisy \textit{labels}.
The noise level of the labels can be controlled by the number of inner replications in the inner simulation model.
One can train supervised learning models using these simulated features and labels.
They are then used to replace the time-consuming inner simulations by the trained model.
We refer to the trained supervised learning models as \textit{metamodels} of the inner simulation, which is also known as the \textit{surrogate models} in the simulation literature.
Metamodeling is a popular approach to reduce the computational burden of simulation-based applications by replacing the time-consuming simulation with a metamodel.
The metamodel is trained using a set of simulated data, and it is used to predict the simulation output for new inputs.
The study of metamodeling is an active research area in the simulation literature, and using \gls{dnn}s as metamodels is a relatively new development.
~\cite{fonseca2003simulation} provide general guidelines for simulation metamodeling with neural networks,~\cite{lieu2022adaptive} use \gls{dnn}s as metamodels of a simulation model for a structural reliability analysis, and~\cite{salle2014efficient} show that neural network metamodels help achieve higher degree of prediction accuracy that other metamodels in approximating agent-based simulation models.
A popular metamodel in nested simulation procedures is stochastic kriging.
~\cite{liu2010stochastic} use stochastic kriging as a metamodel of Monte Carlo simulations to estimate the \gls{cvar} of a portfolio of derivative securities, and~\cite{gan2015valuation} use a stochastic kriging for an efficient valuation of large portfolios of \gls{va} contracts.
Other studies, such as ~\cite{broadie2015risk},~\cite{hong2017kernel}, and~\cite{zhang2022sample} use a regression, a kernel smoothing, and a likelihood ratio method, respectively as metamodels.
Our study has three key distinctions over the existing ones:
\begin{enumerate}
    \item  our metamodel has high-dimensional inputs. In machine learning terminology, the features are high-dimensional vectors.
    To estimate the hedging error of a typical \gls{va} contract, the number of features is in the order of hundreds, which is at least one order of magnitude larger than the number of features in the aforementioned studies,
    \item  for estimating tail risk measures, our metamodel is only used for tail scenario identification but is \textit{not} used in the estimation of the tail risk measures.
    This is a feature designed particularly to convince regulators that the losses used in estimating the risk measure are based on a transparent inner simulation model rather than on some black-box metamodels, and
    \item  using simulation models as data generators, we can decrease the noise level and get arbitrarily close to the true labels by increasing the number of replications in the simulation model.
    This design allows a systematic study of the effect of noisy training labels on the performance of \gls{dnn} models in predicting the noiseless labels.
\end{enumerate}

@@

Consider hedging a \gls{va} contract whose sub-account is invested in a stock, and the hedging portfolio is rebalanced monthly.
At $t \leq T$, a dynamic equation can be specified for the sub-account value $F_t$, in the absence of withdrawals, as:
\begin{equation*}
    F_t = F_{t-1} \cdot \frac{S_t}{S_{t-1}} \cdot (1-\eta_g)
\end{equation*}
where $\eta_g> \eta_n$ is the gross rate of management fee that is deducted from the sub-account value at the end of each month.
The delta hedge portfolio at any month~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at $T$ months.
The value of the hedge portfolio at month~$(t-1)$ is:
\begin{equation*}
    H_{t-1} = \Delta_{t-1} S_{t-1} + B_{t-1},
\end{equation*}
where $S_t$ is an underlying stock price and any month $t>0$.
Assuming there is no rebalacing between $t-1$ and $t$, this hedge portfolio is brought forward to month~$t$,.
Its value at month~$t$ becomes:
\begin{equation*}
    H_{t}^{bf} = \Delta_{t-1} S_{t} + B_{t-1}e^{-rt}.
\end{equation*}
Therefore, the time~$t$ hedging error, which is the cash flow incurred by the insurer due to rebalancing at time~$t$, is
\begin{equation}\label{eq2:hedgingerror}
    HE_t = H_t - H^{bf}_t, \quad t=1,\ldots, T-1.
\end{equation}
The \gls{pl} of the \gls{va} contract includes cost of the initial hedge ($H_0$), hedging errors~\eqref{eq2:hedgingerror}, unwinding of the hedge at maturity ($H^{bf}_T$), and unhedged liability ($V_0$).
Mathematically, the present value of these cash flows is given by
\begin{equation}\label{eq2:lossrv}
L = H_0 + \sum_{t=1}^{T-1} e^{-rt} HE_t - e^{-rT} H^{bf}_T + V_0 = \sum_{t=0}^{T-1}\Delta_t (e^{-rt}S_t - e^{-r(t+1)}S_{t+1}) + V_0,
\end{equation}
where the second equality holds by a telescopic sum simplification of $e^{-rt}B_t$, $t=0,\ldots,T-1$.

In~\eqref{eq2:lossrv}, $\Delta_t$ and $V_0$ are determined by using a risk-neutral measure $\mathbb{Q}$ while the distribution of $L$ is under a real-world measure $\mathbb{P}$.
If $\Delta_t$ and $V_0$ cannot be calculated analytically, a nested simulation is required to estimate the tail risk measure of $L$.
Recall from Section~\ref{subsec:VApayout} that the stock sample path, regardless of the inner or outer simulation or a combination of both, determines the evolution of the triplet $(S_t,F_t,G_t)$.
Specifically, the outer scenarios $\bS^{(i)} = (S_{1}^{(i)},\ldots,S_{T}^{(i)})$, $i=1,\ldots,M$ are generated under $\mathbb{P}$.
At each time~$t=1,\ldots,T-1$ of a given outer scenario $\bS^{(i)}$, inner sample paths $\bStilde_{t}^{(j)} = (\Stilde_{t+1}^{(j)},\ldots,\Stilde_{T}^{(j)})$, $j=1,\ldots,N$ are generated under $\mathbb{Q}$ to estimate $\Delta_t^{(i)}$, $i=1,\ldots,M$.
Also, $V_0^{(i)}$, $i=1,\ldots,M$ are estimated under $\mathbb{Q}$ via inner simulations at time $0$.
Recall from Section~\ref{subsec:VApayout} that the stock's sample path, regardless of inner or outer simulation or a combination of both, determines the evolution of the triplet $(S_t,F_t,G_t)$.
For \gls{gmwb}, a standard nested simulation procedure to estimate the $\alpha$-\gls{cvar} of $L$ is described in Algorithm~\ref{alg2:standardProcedure} below.

>>>>

\gls{dnn} have attracted attentions of researchers and practitioners due to their success~\citep{hastie2009elements,lecun2015deep} in solving real-world machine learning tasks such as AlphaGo~\citep{silver2016mastering} and ChatGPT~\citep{chatgpt}.
Since the first artificial neural network model~\citep{mcculloch1943logical} and the first algorithm for training a perceptron~\citep{rosenblatt1958perceptron}, especially after the introduction of backpropagation~\citep{rumelhart1985learning} and the growth of high-performance computing, the field of artificial neural network and deep learning in general has been growing rapidly.
Two specialized neural network architectures that are relevant to our study are \gls{rnn}~\citep{williams1989learning,sutskever2014sequence} and \gls{lstm}~\citep{hochreiter1997long,chung2014empirical}.
Despite their success, \gls{dnn} models are often criticized for their lack of transparency and interpretability, which hinders their adoption in financial and actuarial applications.
Enormous research efforts have been spent to test and improve the robustness of \gls{dnn} models with carefully designed noise injection methods.
~\cite{poole2014analyzing} show that injecting synthetic noise before and after hidden unit activations during training improves the performance of autoencoders.
~\cite{neelakantan2015adding} improve learning for \gls{dnn}s by injecting synthetic noise to the gradients during backpropagations.
A branch of research has been devoted to understanding the resilience of neural network models to noise in training labels.
For example,~\cite{luo2016understanding} show that adding synthetic label noise to the convolutional neural network (\gls{cnn}) can improve its ability to capture global features. 
~\cite{srivastava2014dropout} quantify the error tolerance by injecting synthetic label noise with a custom Boltzmann machine hardware.
~\cite{szegedy2013intriguing} find that neural networks are vulnerable to adversarial examples, and~\cite{goodfellow2014explaining} design an efficient method to generate such noisy examples to exploit the vulnerability to adversarial perturbations.
~\cite{carlini2017towards} design targeted attacks to training labels to test the robustness of neural networks. 
Instead of using synthetic noise, ~\cite{jiang2020beyond} inject real-world label noise and examine noise tolerance of neural networks with controlled noise levels.
The aforementioned studies use real-world data, as is typically the case for many neural network studies, where noise is already present in the training labels before any noise injection.
Users of real-world data have little control over the noise level of the original training labels and usually examine the effect of noisy data by injecting noise, but it is unclear whether a neural network model trained on noisy data actually learns the real, i.e., noiseless, feature-label relationship.
Due to their lack of transparency and interpretability, the adoption of \gls{dnn}s in financial and actuarial applications has been received by regulators with some skepticism.

@@

Estimating tail risk measures of portfolios of complex \gls{va}s usually requires nested simulation.
In the nested simulation, the outer simulation involves projecting scenarios of key risk factors under a $\mathbb{P}$ measure, while the inner simulations are used to value payoffs uder guarantees of varying complexity, under a $\mathbb{Q}$ measure.

For insurers, large-scale nested simulations for assessing \gls{va} losses are generally computationally intensive; i.e., a large number of outer level simulations are needed to estimate extreme tails for calculations of tail risk measures, and a large number of inner simulations are also needed at each time step, because the embedded options are out of money. 
In addition, the required calculations need to be repeated for each \gls{va} contract, or cluster of \gls{va} contracts.
Consequently, insurers are interested in techniques for nested simulation models that produce accurate results within the confines of a finite computational budget.

There are two main approaches that can be used to improve the efficiency of inner simulations.
The first one uses a dynamic, non-uniform allocation of the inner simulation budget, and the second uses a proxy model to replace the inner simulation step.
Some work uses a combination of both approaches.

In Chapter~\ref{chap:project1}, the likelihood ratio approach is used to allocate the inner simulation budget using likelihood ratio weights, i.e., importance sampling.
Proxy models are tractable analytic functions or flexible empirical functions that are used to replace the inner simulation stage of a nested simulation.
Empirical proxies may be intrinsic or extrinsic to the simulation process. Extrinsic proxy functions are selected to be close to the inner simulation values and therefore require detailed information about the payoffs that are evaluated in the inner simulation step. 
Empirical proxies are constructed by using an initial pilot simulation to develop factors or functionals that can subsequently be used in place of the inner simulation. 
A prominent expirical proxy method discussed in the literature is the least squares Monte Carlo method~\citep{longstaff2001valuing}.
In Chapter~\ref{chap:project1}, supervised learning models, including linear regression, \gls{knn}, and \gls{krr}, are used as proxy models for inner simulations.
This chapter introduces a proxy model to reduce the computational requirements of inner simulations of \gls{va}s by replacing the inner simulation step of a nested simulation procedure. 
This proxy model is chosen to be a flexible empirical function, i.e., a \gls{dnn} metamodel.

In our study, supervised learning metamodels are trained using data simulated from an initial pilot simulation.
They are then used to replace the time-consuming inner simulations by the trained model.
Borrowing terminologies from the machine learning community, we can view a set of simulated outer scenarios and estimated hedging errors for those scenarios as \textit{features} and noisy \textit{labels}.
The noise level of the labels can be controlled by the number of inner replications in the inner simulation model.
We refer to the trained supervised learning proxy models as \textit{metamodels} of the inner simulation, which is also known as the \textit{surrogate models} in the simulation literature.
Metamodeling is a popular approach to reduce the computational burden of simulation-based applications by replacing the time-consuming simulation with a metamodel.
The metamodel is trained using a set of simulated data, and it is used to predict the simulation output for new inputs.
The study of metamodeling is an active research area in the simulation literature, and using \gls{dnn}s as metamodels is a relatively new development.
~\cite{fonseca2003simulation} provide general guidelines for simulation metamodeling with neural networks,~\cite{lieu2022adaptive} use \gls{dnn}s as metamodels of a simulation model for a structural reliability analysis, and~\cite{salle2014efficient} show that neural network metamodels help achieve higher degree of prediction accuracy that other metamodels in approximating agent-based simulation models.
A popular metamodel in nested simulation procedures is stochastic kriging.
~\cite{liu2010stochastic} use stochastic kriging as a metamodel of Monte Carlo simulations to estimate the \gls{cvar} of a portfolio of derivative securities, and~\cite{gan2015valuation} use a stochastic kriging for an efficient valuation of large portfolios of \gls{va} contracts.
Other studies, such as ~\cite{broadie2015risk},~\cite{hong2017kernel}, and~\cite{zhang2022sample} use a regression, a kernel smoothing, and a likelihood ratio method, respectively as metamodels.
Our study has three key distinctions over the existing ones:
\begin{enumerate}
    \item  our metamodel has high-dimensional inputs. In machine learning terminology, the features are high-dimensional vectors.
    To estimate the hedging error of a typical \gls{va} contract, the number of features is in the order of hundreds, which is at least one order of magnitude larger than the number of features in the aforementioned studies,
    \item  for estimating tail risk measures, our metamodel is only used for tail scenario identification but is \textit{not} used in the estimation of the tail risk measures.
    This is a feature designed particularly to convince regulators that the losses used in estimating the risk measure are based on a transparent inner simulation model rather than on some black-box metamodels, and
    \item  using simulation models as data generators, we can decrease the noise level and get arbitrarily close to the true labels by increasing the number of replications in the simulation model.
    This design allows a systematic study of the effect of noisy training labels on the performance of \gls{dnn} models in predicting the noiseless labels.
\end{enumerate}

@@

Consider hedging a \gls{va} contract whose sub-account is invested in a stock, and the hedging portfolio is rebalanced monthly.
At $t \leq T$, a dynamic equation can be specified for the sub-account value $F_t$, in the absence of withdrawals, as:
\begin{equation*}
    F_t = F_{t-1} \cdot \frac{S_t}{S_{t-1}} \cdot (1-\eta_g)
\end{equation*}
where $\eta_g> \eta_n$ is the gross rate of management fee that is deducted from the sub-account value at the end of each month.
The delta hedge portfolio at any month~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at $T$ months.
The value of the hedge portfolio at month~$(t-1)$ is:
\begin{equation*}
    H_{t-1} = \Delta_{t-1} S_{t-1} + B_{t-1},
\end{equation*}
where $S_t$ is an underlying stock price and any month $t>0$.
Assuming there is no rebalacing between $t-1$ and $t$, this hedge portfolio is brought forward to month~$t$,.
Its value at month~$t$ becomes:
\begin{equation*}
    H_{t}^{bf} = \Delta_{t-1} S_{t} + B_{t-1}e^{-rt}.
\end{equation*}
Therefore, the time~$t$ hedging error, which is the cash flow incurred by the insurer due to rebalancing at time~$t$, is
\begin{equation}\label{eq2:hedgingerror}
    HE_t = H_t - H^{bf}_t, \quad t=1,\ldots, T-1.
\end{equation}
The \gls{pl} of the \gls{va} contract includes cost of the initial hedge ($H_0$), the periodic hedging gains and losses due to rebalancing at each time $t=1,\ldots,T-1$ (Equation~\ref{eq2:hedgingerror}), unwinding of the hedge at maturity ($H^{bf}_T$), the payment of guaranteed benefit, and the management fee income.
The present value of these cash flows, discounted at the risk-free rate, is the insurer's overall \gls{pl} from the \gls{va} contract.
At $t=0$, the insurer's overall \gls{pl}, i.e., the loss random variable $L$ to which a risk measure is applied, is given by
\begin{align}\label{eq2:lossrvtw}
L & = H_0 + \sum_{t=1}^{T-1} e^{-rt} HE_t - e^{-rT} H^{bf}_T + V_0  \nonumber \\
  & = H_0 + \sum_{t=1}^{T-1} e^{-rt} (H_t - H_t^{bf}) - e^{-rT} H^{bf}_T + V_0  \nonumber \\
  & = B_0 + S_0 V_0 + \sum_{t=1}^{T-1} e^{-rt} \left( B_t + S_t \Delta_t - B_{t-1} \frac{e^{-r(t-1)}}{e^{-rt}} - S_{t-1} \Delta_{t-1}  \right) - e^{-rT} S_T \Delta_{T-1} + V_0,  \nonumber 
\end{align}
where $V_0$ can be thought of as a discounted payoff of the \gls{va} contract at $t=0$, net of fee income in the absense of any hedging.
The terms $H_0 + \sum_{t=1}^{T-1} e^{-rt} HE_t - e^{-rT} H^{bf}_T$ is the gain or loss from hedging.
It consists of three components:
\begin{itemize}
    \item   $H_0$ is the initial cost of the hedging portfolio, 
    \item   $\sum_{t=1}^{T-1} e^{-rt} HE_t$ is the gain or loss from all rebalacing trades at time $t=1,\ldots,T-1$, and
    \item   $-e^{-rT} H^{bf}_T$ is the proceeds from unwinding the hedge at maturity $T$.
\end{itemize}
Rearranging the terms in Equation~\ref{eq2:lossrvtw}, the loss random variable $L$ can be simplified as
\begin{equation}\label{eq2:lossrv}
    L = \sum_{t=0}^{T-1}\Delta_t (e^{-rt}S_t - e^{-r(t+1)}S_{t+1}) + V_0.
\end{equation}
Equation~\ref{eq2:lossrv} shows that in bond holdings of hedging portfolio, all intermediate bond transactions cancel out since the interest rate $r$ at which bond value accumulates is the same as rate at which \gls{pl}s from bond transactions are discounted. 
In the stock holdings of the hedging portfolio, the gain or loss arises from the inital set-up of stock future holdings and the \gls{pl} from each rebalancing trade.
In~\eqref{eq2:lossrv}, $\Delta_t$ and $V_0$ are determined by using a risk-neutral measure $\mathbb{Q}$ while the distribution of $L$ is under a real-world measure $\mathbb{P}$.
If $\Delta_t$ and $V_0$ cannot be calculated analytically, a nested simulation is required to estimate the tail risk measure of $L$.
Specifically, the outer scenarios $\bS^{(i)} = (S_{1}^{(i)},\ldots,S_{T}^{(i)})$, $i=1,\ldots,M$ are generated under $\mathbb{P}$ measures to estimate the loss distribution.
At each time~$t=1,\ldots,T-1$ of a given outer scenario $\bS^{(i)}$, inner sample paths $\bStilde_{t}^{(j)} = (\Stilde_{t+1}^{(j)},\ldots,\Stilde_{T}^{(j)})$, $j=1,\ldots,N$ are generated under $\mathbb{Q}$ to estimate $\Delta_t^{(i)}$, $i=1,\ldots,M$.
Also, $V_0^{(i)}$, $i=1,\ldots,M$ are estimated under $\mathbb{Q}$ via inner simulations at time $0$.
Recall from Section~\ref{subsec:VApayout} that the stock's sample path, regardless of inner or outer simulation or a combination of both, determines the evolution of the triplet $(S_t,F_t,G_t)$.
For \gls{gmwb}, a standard nested simulation procedure to estimate the $\alpha$-\gls{cvar} of $L$ is described in Algorithm~\ref{alg2:standardProcedure} below.
